Disturbance-aware minimum-time planning strategies for motorsport vehicles with probabilistic safety certificates

### 2025-05-02 intro.tex
[MGa] some notes in intro

\subsection{Related work}
In recent years, extensive research has been conducted on ... 
\subsection{Paper's contributions}
In this study, we investigate ...

>>>>

Some key aspects: The omission of explicit disturbance modeling within the planning framework can critically compromise the satisfaction of operational constraints. In particular, time-optimal planning algorithms frequently yield trajectories that lie in close proximity to constraint boundaries, such as those associated with collision avoidance. Under such conditions, even small perturbations may induce constraint violations, thereby significantly jeopardizing system safety. Although the introduction of fixed, heuristically selected safety margins around constraint sets may offer a nominal safeguard, this strategy does not provide formal assurances of constraint satisfaction under perturbations and often leads to overly conservative and suboptimal solutions.

\subsection{Related work}
In recent years, extensive research has been conducted on ...

\subsection{Paper's contributions}
In this study, we investigate ...
